meta2pred

### 2019-10-04 meta_info_collec/metafun/meta2preds.Rmd
look @ meta-predictors for cds & aug cds

```{r}
# N50
bp + geom_point(aes(x=N50, y=acc_overall))
bp + geom_point(aes(x=N50, y=f1_total_1))
```

@@

@@

>>>>

```{r}
# N50
bp + geom_point(aes(x=N50, y=acc_overall))
bp + geom_point(aes(x=N50, y=f1_total_1))
bp + geom_point(aes(x=N50, y=f1_cds_1))
```

@@

## now for Augustus (Marvin's internship results)

### first: f1_cds_1 on the same subset of genomes but with pred 9
```{r}
# these are basically all the input vars
aug <- read.csv('Augustus_results.csv')
plus_aug <- merge(prepreg_scale, aug, by.x="species", by.y="genome")
x <- plus_aug[, c(to_scale, FALSE)]  # new f1_cds_1_RT column is not scaled
#x$trained_on <- plus_aug$trained_on
x$y <- logit(plus_aug$f1_cds_1)
pls.f1_cds_1.fit <- plsr(y~., data=x)
validationplot(pls.f1_cds_1.fit)
```

```{r}
# viz prediction accuracy
plot(x$y, predict(pls.f1_cds_1.fit, x, ncomp=3))
plot(x$y, predict(pls.f1_cds_1.fit, x, ncomp=12))
```

```{r}
# loadings
mc_aug <- metaclass[-length(metaclass)]
plot_with_loadings(pls.f1_cds_1.fit, mc_aug)
```

#### looking at final coeffs with ncomp=2+
```{r}
plot_with_ncomps(2, pls.f1_cds_1.fit, mc_aug)
plot_with_ncomps(3, pls.f1_cds_1.fit, mc_aug)
plot_with_ncomps(9, pls.f1_cds_1.fit, mc_aug)
plot_with_ncomps(16, pls.f1_cds_1.fit, mc_aug)
```

### now for Augustus

```{r}
# these are basically all the input vars
x <- plus_aug[, c(to_scale, FALSE)]  # new f1_cds_1_RT column is 
x$y <- logit(plus_aug$f1_cds_1_RT)
pls.f1_cds_1_RT.fit <- plsr(y~., data=x)
validationplot(pls.f1_cds_1_RT.fit)
```
```{r}
# viz prediction accuracy
plot(x$y, predict(pls.f1_cds_1_RT.fit, x, ncomp=3))
plot(x$y, predict(pls.f1_cds_1_RT.fit, x, ncomp=12))
```
```{r}
# loadings
# skip trained_on for metaclass
plot_with_loadings(pls.f1_cds_1_RT.fit, mc_aug)
```
#### looking at final coeffs with ncomp=2+
```{r}
plot_with_ncomps(2, pls.f1_cds_1_RT.fit, mc_aug)
plot_with_ncomps(3, pls.f1_cds_1_RT.fit, mc_aug)
plot_with_ncomps(9, pls.f1_cds_1_RT.fit, mc_aug)
plot_with_ncomps(16, pls.f1_cds_1_RT.fit, mc_aug)
```

@@

Lucikly it looks like our training genomes are fairly well distributed in
terms of kmers.
```{r}
source('scripts/PCA.R')
```
